Unicode Implementation Issues \thanks { This is a working document for the Rexx Language Association (RexxLA). There will be one or more separate requirements documents. It is written in \LaTeX\ \fmtversion\ and was rendered \today\ using \enginedetails. }

### 2024-04-12 ARB/standards/work-in-progress/document/tex/standard/conformance.tex
work in standard book production process including readme.md
upd
add filenames

\hypertarget{conformance}{%
\chapter{Conformance}\label{conformance}}

\hypertarget{conformance-1}{%
\section{Conformance}\label{conformance-1}}

@@

\begin{itemize}
\item
  alist of all definitions or values for the features in this standard
  which are specified to be dependent on the configuration.
\item
  a statement of conformity, giving the complete reference of this
  standard (ANSI X3.274-1996) with which conformity is claimed.
\end{itemize}

\hypertarget{limits}{%
\section{Limits}\label{limits}}

Aside from the items listed here (and the assumed limitation in
resources of the configuration), a conforming language processor shall
not put numerical limits on the content of a program. Where a limit
expresses the limit on a number of digits, it shall be a multiple of
three. Other limits shall be one of the numbers one, five or twenty
five, or any of these multiplied by some power of ten. Limitations that
conforming language processors may impose are:

\begin{itemize}
\item
  NUMERIC DIGITS values shall be supported up to a value of at least
  nine hundred and ninety nine.
\item
  Exponents shall be supported. The limit of the absolute value of an
  exponent shall be at least as large as the largest number that can be
  expressed without an exponent in nine digits.
\item
  String lengths shall be supported. The limit on the length shall be at
  least as large as the largest number that can be expressed without an
  exponent in nine digits.
\item
  String literal length shall be supported up to at least two hundred
  and fifty.
\item
  Symbol length shall be supported up to at least two hundred and fifty.
\end{itemize}

>>>>

%preprocessed texin
\chapter{Conformance}\label{conformance}

\section{Conformance}\label{conformance-1}

@@

\begin{itemize}
\item
  a list of all definitions or values for the features in this standard
  which are specified to be dependent on the configuration.
\item
  a statement of conformity, giving the complete reference of this
  standard (ANSI X3.274-1996) with which conformity is claimed.
\end{itemize}

\section{Limits}\label{limits}

Aside from the items listed here (and the assumed limitation in
resources of the configuration), a conforming language processor shall
not put numerical limits on the content of a program. Where a limit
expresses the limit on a number of digits, it shall be a multiple of
three. Other limits shall be one of the numbers one, five or twenty
five, or any of these multiplied by some power of ten.

Limitations that conforming language processors may impose are:

\begin{itemize}
\item
  \texttt{NUMERIC\ DIGITS} values shall be supported up to a value of at
  least nine hundred and ninety nine.
\item
  Exponents shall be supported. The limit of the absolute value of an
  exponent shall be at least as large as the largest number that can be
  expressed without an exponent in nine digits.
\item
  String lengths shall be supported. The limit on the length shall be at
  least as large as the largest number that can be expressed without an
  exponent in nine digits.
\item
  String literal length shall be supported up to at least two hundred
  and fifty.
\item
  Symbol length shall be supported up to at least two hundred and fifty.
\end{itemize}

### 2024-04-12 ARB/standards/work-in-progress/document/tex/standard/definitions_and_document_notation.tex
add filenames

Lots more for NetRexx

@@

function call or following the name on a CALL instruction. Also the
corresponding values which may be accessed by a function or routine,

@@

functions, such as D2C.

@@

A specific event, or state, which can be trapped by CALL ON or SIGNAL
ON.

@@

A named syntax grouping, for example ``expression'', ``do\_
specification''.

@@

The relation between a character string anda corresponding number. The

@@

externally but then alterable by using the ADDRESS instruction.

@@

accessed by the VALUE built-in function.

@@

A function or subroutine that is in the same program as the CALL
instruction or function call that invokes it.

>>>>

\emph{Lots more for NetRexx}

@@

function call or following the name on a \texttt{CALL} instruction. Also
the corresponding values which may be accessed by a function or routine,

@@

functions, such as \texttt{D2C}.

@@

A specific event, or state, which can be trapped by \texttt{CALL\ ON} or
\texttt{SIGNAL\ ON}.

@@

A named syntax grouping, for example ``\emph{expression}'',
``\emph{do\_specification}''.

@@

The relation between a character string and a corresponding number. The

@@

externally but then alterable by using the \texttt{ADDRESS} instruction.

@@

accessed by the \texttt{VALUE} built-in function.

@@

A function or subroutine that is in the same program as the
\texttt{CALL} instruction or function call that invokes it.
